Harnessing the cloud to understand light: A whitepaper detailing the \MaxwellFDS core solver

### 2013-05-28 thesis/intro.tex
Ready to submit thesis to committee.
Minor correction (from Jelena).

Built upon this prior art,
    this work's aim is to produce a design method 
    that not only produces designs for a single device,
    but for a wide range of devices.
Specifically,
    we desired to be able to produce devices which
    \BI have very compact footprints,
    \I  exhibit high efficiency performance,
    \I  are multi-modal in their operation,
    \I  are robust to shifts in wavelength and temperature,
    \I  are robust to fabrication error,
    \I  may even demonstrate novel, never-before-seen functionality. \EI
Our final result (chapter~\ref{final}) indeed demonstrates
    manufacturable, three-dimensional nanophotonic devices which
    exhibit these properties.

@@

The organization of this thesis is straightforward: 
    chapters \ref{direct}-\ref{ob-1} detail the incremental steps in achieving
    our final result, which is presented in chapter \ref{final}.
Futhermore, each section is broken into three major sections:
    \begin{description}
    \item[Problem formulation] where we show how we cast the design problem
        in incrementally more sophisticated mathematics.
    \item[Implementation] where we note how the formulated problem 
        was solved computationally.
    \item[Results] where we demonstrate the abilities (and weaknesses)
        of each formulation.
    \end{description}

@@

The work presented here is based on the following publications:
\begin{itemize}
\item chapters~\ref{direct}-\ref{bounded}: ``Inverse design of nanophotonic structures using complementary convex optimization,'' Opt. Express (2010),
\item chapter~\ref{bounded}:
    ``Inverse design of a three-dimensional nanophotonic resonator,''
    Opt. Express (2011), 
\item chapter~\ref{ob-1}: ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
    Opt. Express (2012),
\item chapter~\ref{final}: ``Nanophotonic computational design,'' Opt. Express (2013).
\end{itemize}

>>>>

Built upon this prior art,
    this work's aim is to produce a design method 
    that not only produces designs for a single device,
    but for a wide range of devices.
Specifically,
    we desired to be able to produce devices which
    \BI have very compact footprints,
    \I  exhibit high efficiency performance,
    \I  are multi-modal in their operation,
    \I  are robust to shifts in wavelength and temperature,
    \I  are robust to fabrication error,
    \I  demonstrate novel, never-before-seen functionality. \EI
Our final result (chapter~\ref{final}) indeed demonstrates
    manufacturable, three-dimensional nanophotonic devices which
    exhibit these properties.

@@

The organization of this thesis is straightforward: 
    chapters \ref{direct}-\ref{ob-1} detail the incremental steps in achieving
    our final result, which is presented in chapter \ref{final}.
Futhermore, each chapter is broken into three major sections:
    \begin{description}
    \item[Problem formulation] where we show how we cast the design problem
        in incrementally more sophisticated mathematics.
    \item[Implementation] where we note how the formulated problem 
        was solved computationally.
    \item[Results] where we demonstrate the abilities (and weaknesses)
        of each formulation.
    \end{description}

@@

The work presented here is based on the following publications:
\begin{itemize}
\item chapters~\ref{direct}-\ref{bounded}: J. Lu and J. Vuckovic, ``Inverse design of nanophotonic structures using complementary convex optimization,'' Opt. Express \textbf{18}, 3793-3804 (2010),
\item chapter~\ref{bounded}: J. Lu, S. Boyd, and J. Vuckovic, 
    ``Inverse design of a three-dimensional nanophotonic resonator,''
    Opt. Express \textbf{19}, 10563-10750 (2011),
\item chapter~\ref{ob-1}: J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
    Opt. Express \textbf{20}, 7221-7236 (2012),
\item chapter~\ref{final}: J. Lu, J. Vuckovic, ``Nanophotonic computational design,'' 
    Opt. Express \textbf{21}, 13351-13367 (2013).
\end{itemize}
